Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
Removed I_2 and added names to all inequalities that remained

    The first causal compatibility inequality is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e. factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}. As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}. Notice the first term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $+1$. For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $0.0129\ldots \not \leq 0$. Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.

    To reiterate, the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary} and more details can be found in \cref{sec:exemplary_inflations_of_the_triangle structure}.

    It is possible to simplify \cref{eq:ww_ineq} by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$. Upon doing so, one obtains the following,
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq_symplified}
        + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
        - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
        - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}

    In order to understand the importance of \cref{eq:ww_ineq}, there are a couple of important concepts to understand. First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$. The inequality of \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure. For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$. Furthermore, the existence of an inequality capable of witnessing the non-classicality of the Fritz distribution is guaranteed and the Inflation Technique is capable of producing such an inequality~\cite{Navascues_2017}, albeit requiring a sufficiently complex inflation of the Triangle structure. In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and others were \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution. This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle structure. More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.

    In addition to \cref{eq:ww_ineq}, numerous independent inequalities were derived for the Triangle structure that are violated by the Fritz distribution. The majority of these inequalities share most or all of the qualitative features of \cref{eq:ww_ineq}, and hence those inequalities are omitted from this manuscript. Instead, we present \cref{eq:web_inequality}, another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the \cref{fig:the_web_inflation} --- a considerably larger inflation than the Wagon-Wheel inflation. Note that in \cref{eq:web_inequality} $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.

    \begin{equation}
        \label{eq:web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{equation}

    The inequalities presented above (\cref{eq:ww_ineq,eq:web_inequality}) were curated to demonstrate the incompatibility of the Fritz distribution in particular. To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$. The asymmetry within the Fritz distribution is reflected in the asymmetry of \cref{eq:ww_ineq,eq:web_inequality}. In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality (i.e. inequalities) that do not admit this bias. In an effort to find a causal compatibility inequality qualitatively distinct from \cref{eq:ww_ineq,eq:web_inequality}, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$. These techniques are explained in \cref{sec:symmetric_inequalities}. Surprisingly, \cref{eq:symmetic_web_inequality} is also violated by the Fritz distribution.
    \begin{equation}
        \label{eq:symmetic_web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{equation}
    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e. $\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.

    Most importantly, these causal compatibility inequalities are a positive resolution of Fritz's problem from \cref{sec:fritz_distribution}. These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a causal inference perspective. Additionally, the derivation of causal compatibility inequalities prove incompatibility even when perfect correlations are absent.

@@

    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ such that $I\br{\prob} < 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality). For the subsequent analysis, $4$ inequalities where chosen. First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}. The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}. Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.

@@

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$. Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible. We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.  Our tests suggest that inequality $I_1$ (\cref{eq:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.

@@

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately. In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states. Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix. Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure. Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

@@

    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{eq:web_inequality} ($V_F \simeq 1.501$).}
            \label{fig:maximum_violation_I_1}
    \end{center}
    \end{figure}
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{eq:symmetic_web_inequality} ($V_F \simeq 2.61$).}
            \label{fig:maximum_violation_I_3}
    \end{center}
    \end{figure}
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
            \label{fig:symmetrized_fritz}
    \end{center}
    \end{figure}

    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e. $V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$. The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}. At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$. Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution. In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e. the same set of possible events. This result is not entirely unexpected. As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure. Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.

    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization. Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries. Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation} which is achievable by the Fritz distribution $\prob[\fritz]$. Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (i.e. any non-unique set of parameters that induce the Fritz distribution) were able to achieve violation. Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence. Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods. Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization. More likely, this phenomena is due to a combination of both effects.

>>>>

    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle structure}.

    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e. factorizes according to \cref{eq:triangle_compatibility}) must satisfy $I\tsb{WagonWheel}$. As a demonstration, the first term in \cref{eq:ww_ineq} for the Fritz distribution is $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ while all of the remaining terms sum to $\simeq 0.0136$. Therefore, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $0.0129\ldots \not \leq 0$. Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.

    It is possible to simplify $I\tsb{WagonWheel}$ by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$. Upon doing so, one obtains an equivalent representation for $I\tsb{WagonWheel}$,
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq_symplified}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
    - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
    - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}

    In order to understand the importance of $I\tsb{WagonWheel}$, there are a couple of important concepts to understand. First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$. The inequality of $I\tsb{WagonWheel}$ represents a significant advancement in our understanding of non-classicality in the Triangle structure. For example, $I\tsb{WagonWheel}$ is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$. Furthermore, the existence of an inequality capable of witnessing the non-classicality of the Fritz distribution is guaranteed and the Inflation Technique is capable of producing such an inequality~\cite{Navascues_2017}, albeit requiring a sufficiently complex inflation of the Triangle structure. In fact, $I\tsb{WagonWheel}$ was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and others were \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution. This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as $I\tsb{WagonWheel}$ strong enough to witness incompatible quantum distributions for the Triangle structure. More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.

    In addition to $I\tsb{WagonWheel}$, numerous independent inequalities were derived for the Triangle structure that are violated by the Fritz distribution. The majority of these inequalities share most or all of the qualitative features of $I\tsb{WagonWheel}$, and hence those inequalities are omitted from this manuscript. Instead, we present $I\tsb{Web}$ (\cref{eq:web_inequality}), another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the Web inflation (\cref{fig:the_web_inflation}) --- a considerably larger inflation than the Wagon-Wheel inflation. Note that in \cref{eq:web_inequality} $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.

    \begin{equation}
    \label{eq:web_inequality}
    \begin{gathered}
        I\tsb{Web} : \\
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{gathered}
    \end{equation}

    The inequalities presented above, namely $I\tsb{WagonWheel}$ and $I\tsb{Web}$, were curated to demonstrate the incompatibility of the Fritz distribution in particular. To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$. The asymmetry within the Fritz distribution is reflected in the asymmetry of $I\tsb{WagonWheel}$ and $I\tsb{Web}$. In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality, such as inequalities, that do not admit this bias. In an effort to find a causal compatibility inequality qualitatively distinct from $I\tsb{WagonWheel}$ or $I\tsb{Web}$, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$. These techniques are explained in \cref{sec:symmetric_inequalities}. Surprisingly, \cref{eq:symmetic_web_inequality} is also violated by the Fritz distribution.
    \begin{equation}
        \label{eq:symmetic_web_inequality}
    \begin{gathered}
        I\tsb{SymmetricWeb} : \\
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{gathered}
    \end{equation}
    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e. $\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.

    Most importantly, these causal compatibility inequalities are a positive resolution of Fritz's problem from \cref{sec:fritz_distribution}. These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a more universal causal inference perspective.

@@

    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ into the format of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetic_web_inequality} where the linear combination of all terms is upper-bound by $0$. For each inequality $I$ and distribution $\prob$, $I\br{\prob}$ denotes the numerical value associated with this upper-bound. Correspondingly, $I\br{\prob} > 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).

@@

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$, which is trivially compatible with the Triangle structure. The objective of this section is to quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before the reported inequalities fail to witness incompatibility. The associated quantifier used was an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ where $\s{N}_{\vep}$ denotes an \term{$\vep$-noisy Fritz distribution},
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    As $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. Our tests suggest that $I\tsb{Web}$ is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I\tsb{Web}$; an exhaustive search has not been conducted.

@@

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately. In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix. Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for generating incompatible quantum distributions in the Triangle structure. Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

@@

    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I\tsb{Web}$ ($V_F \simeq 1.501$).}
            \label{fig:maximum_violation_I_1}
    \end{center}
    \end{figure}
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I\tsb{SymmetricWeb}$ ($V_F \simeq 2.61$).}
            \label{fig:maximum_violation_I_3}
    \end{center}
    \end{figure}
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
            \label{fig:symmetrized_fritz}
    \end{center}
    \end{figure}

    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e. $V_F \defined \max_{P}\bc{I\br{P}/I\br{P_F}}$. The first inequality in consideration is $I\tsb{Web}$. At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$. Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution. In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e. the same set of possible events. This result is not entirely unexpected. As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure. Consequently, it seems that $I\tsb{Web}$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.

    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization. Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries. Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation}. Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (i.e. any non-unique set of parameters that induce the Fritz distribution) were able to achieve violation. Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence. Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods. Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization. More likely, this phenomena is due to a combination of both effects.
